Finding the True MVP

### 2024-12-02 paper/paper.qmd
Created some graphs

library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(knitr)
library(bayesplot)
library(StanHeaders)
library(Matrix)
library(lme4)

@@

```{r}
Real_MVP_Data <- read.csv("../NBAMVP/data/01-raw_data/NBA\\ MVPs/Real_MVP_Data.csv")

@@

merged_real_mvp <- merge(
  Real_MVP_Data, 
  nba_master[, c("Player", "Year", "MVP_index")],  # Select only relevant columns from nba_master
  by = c("Player", "Year"), 
  all.x = TRUE
)

@@

ggplot(mvp_table, aes(x = Year, y = MVP_index)) +
  geom_point(color = "blue", size = 3, alpha = 0.7) +
  labs(
    title = "MVP Index Over the Years",
    x = "Year",
    y = "MVP Index"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14)
  )
```

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(knitr)
library(bayesplot)
library(StanHeaders)
library(Matrix)
library(lme4)
library(patchwork)

@@

```{r}
Real_MVP_Data <- read.csv("../data/01-raw_data/NBA MVPs/Real_MVP_Data.csv")

@@

merged_real_mvp <- merge(
  Real_MVP_Data, 
  nba_master[, c("Player", "Age", "MVP_index")],  # Select only relevant columns from nba_master
  by = c("Player", "Age"), 
  all.x = TRUE
)

merged_real_mvp <- merged_real_mvp %>%
  mutate(
    Year = case_when(
      # If entry matches "YYYY-YY", extract the first 4 characters as the year
      grepl("^\\d{4}-\\d{2}$", Season) ~ as.numeric(substr(Season, 1, 4)) + 1,

      # If entry matches "Mmm-YY", extract the last 2 characters, convert to 20YY, and add 1
      grepl("^[a-zA-Z]{3}-\\d{2}$", Season) ~ as.numeric(paste0("20", substr(Season, 5, 6))) + 1,

      # Default: NA for non-matching formats
      TRUE ~ NA_real_
    )
  )

# Convert Year column to numeric
merged_real_mvp$Year <- as.numeric(merged_real_mvp$Year)

@@

ggplot(merged_real_mvp, aes(x = Year, y = MVP_index)) +
  geom_point(color = "blue", size = 3, alpha = 0.7) +
  labs(
    title = "Scatter: Year vs. MVP Index (Merged Real MVPs)",
    x = "Year",
    y = "MVP Index"
  ) +
  coord_cartesian(ylim = c(1.7, 2.8)) +  # Maintain the same y-axis range
  theme_minimal()

ggplot(mvp_table, aes(x = Year, y = MVP_index)) +
  geom_point(color = "red", size = 3, alpha = 0.7) +
  labs(
    title = "Scatter: Year vs. MVP Index (MVP Table)",
    x = "Year",
    y = "MVP Index"
  ) +
  coord_cartesian(ylim = c(1.7, 2.8)) +  # Maintain the same y-axis range
  theme_minimal()
